Modal Abstractions for Virtualizing Memory Addresses

### 2023-03-01 programlogic.tex
+

Being inspired by what hybrid logic \ref{} calls a satisfaction operator, which evaluates the truth of a predicate in a named alternative state (here, address space), we give a modal definition describing the truth of assertions for the resources inside the address space, $[r]P$ indicating that $P$ holds in the virtual address space rooted at $r$. While doing so, we explain what a modal resource context is, and how it interacts with the ambient logic, i.e. separation logic.
\paragraph{Modal Resource Context}
\label{sec:resourcecontext}
When we pick up a certain contingency, which is \textit{"a certain virtual-pointsto facts whose validity is indexed by the root address of an address space"}for address space modality, we, in fact, make our choice around some logical resources for which we care about reasoning, which is virtual pointsto relation shown in Figure \ref{fig:virtualpointstosharing}.
\paragraph{Interaction}
\label{sec:interaction}

>>>>

Being inspired by what hybrid logic \ref{} calls a satisfaction operator, which evaluates the truth of a predicate in a named alternative state (here, address space), we give a modal definition describing the truth of assertions for the resources inside the address space, $[r]P$ indicating that $P$ holds in the virtual address space rooted at $r$. While doing so, we explain what a modal resource context is, and how it interacts with the ambient logic, i.e. separation logic.
\paragraph{Modal Resource Context}
\label{sec:resourcecontext}
When we pick up a certain contingency, which is \textit{"a certain virtual-pointsto facts whose validity is indexed by the root address of an address space"}for address space modality, we, in fact, make our choice around some logical resources for which we care about reasoning, which is virtual pointsto relation shown in Figure \ref{fig:virtualpointstosharing}. In other words, our modality definition is the logical virtual pointsto resources: introduction/elimination of logical virtual pointsto resources are the ones essential to the reasoning capabilities the address space modality provides, i.e. validity of virtual addresses under/out of modality -- resources under/out of \textit{modal resource context}.  
\paragraph{Interaction}
\label{sec:interaction}
